---
title: "User-and-Website-APIs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{User-and-Website-APIs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## User APIs, Apps APIs

The web interface of Piwik Pro is good for manual setup. But if you need to check
which permissions a specific user has it gets disgusting.

That's when you want to use the various APIs Piwik Pro offers to solve this 
problem programmatically. 

So `piwikproR` was extended by some parts of the users-API and apps-API.

## Which Websites are tracked?

So first, let's fetch a list of websites (called apps in Piwik Pro API).

```{r, eval = FALSE}
library(piwikproR)
# Piwik credentials
piwik_pro_credentials <- list(
  client_id = "my_client_id",
  client_secret = "my_client_secret",
  url = "https://my_site.piwik.pro"
 )
# Fetch a Piwik token
token <- get_login_token(piwik_pro_credentials)
```

### Apps

```{r, eval = FALSE}
apps <- get_apps_list(token) 
```

```{r, echo = FALSE}
apps <- tibble::tribble(
  ~type, ~id, ~name, ~addedAt, ~updatedAt,
  "ppms/meta-site", "some-hex-id-number-1", "site-name-1.com", lubridate::ymd_hms("2022-01-02 08:10:20"), lubridate::ymd_hms("2022-01-04 10:08:10"),
  "ppms/meta-site", "some-hex-id-number-2", "site-name-2.org", lubridate::ymd_hms("2022-02-02 08:10:20"), lubridate::ymd_hms("2022-02-04 10:08:10"),
  "ppms/meta-site", "some-hex-id-number-3", "site-name-3.net", lubridate::ymd_hms("2022-03-02 08:10:20"), lubridate::ymd_hms("2022-03-04 10:08:10")
)
```

The result of `get_apps_list()` is a data.frame containing the available
apps with some information, esp. an id.

```{r}
apps
```

The id can be used for further queries.

### Metasites

Metasites can be fetched similarly:

```{r, eval = FALSE}
metasites <- get_metasites_list(token)
```

```{r, echo = FALSE}
metasites <- tibble::tribble(
  ~type, ~id, ~name, ~created_at, ~updated_at,
  "ppms/apps", "some-hex-id-meta-1", "Meta site 1", lubridate::ymd_hms("2022-01-02 08:10:20"), lubridate::ymd_hms("2022-01-04 10:08:10"),
  "ppms/apps", "some-hex-id-meta-2", "Meta site 2", lubridate::ymd_hms("2022-02-02 08:10:20"), lubridate::ymd_hms("2022-02-04 10:08:10"),
  "ppms/apps", "some-hex-id-meta-3", "Meta site 3", lubridate::ymd_hms("2022-03-02 08:10:20"), lubridate::ymd_hms("2022-03-04 10:08:10")
)
```

The result looks similar. Unfortunately Piwik Pro named the fields slightly differently.

```{r}
metasites
```
# App Details

# Users and Permissions



